A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-21 tex/codatadp.tex
Minor fixes

\paragraph{Phase 3: Branching.}
If a selector is applied to a term $t$, or if $t$'s type is a finite datatype,
the equivalence class of $t$ must contain an application of one of
$\delta$'s constructors
$\Ctr^\delta = \{ \const{C}_1, \ldots, \const{C}_m \}$.
This is enforced in the third phase by the \rn{Split} rule.
A companion rule, \rn{Singleton}, handles the degenerate case where two terms
from $\tEc$ have a corecursive singleton type, in which case they must be
equivalent. Both the finiteness assumption on the datatype in \rn{Split} and
the cardinality-1 constraint on the codatatype in \rn{Singleton} are easy to
check based on a recursive computation of the cardinalities of the
constructors' argument types.

@@

If $t$ is a selector term of the form $\const s^j_k( u )$,
since \rn{Split} does not apply,
$\ec{u}$ must contain a term of the form $\const C_j( \const s^1_j( u ), \ldots, \const s^{n}_j( u ) )$ for some $j$.
By Lemma~\ref{lem:model-completion}.2 and due to our construction of $\Val^\ast$, we have $\Val^\ast \ec{u}$ is of the form
$\MU {\Varec{u}}.\; \const C_l( w_1, \ldots, w_n )$,
where $\Val^\ast \ec{u} \interp{ w_j } = \Val^\ast \ec{ \const s^j_k( u )}$. 
If $k = l$, then $\M( t )$ is $\alpha$-equivalent with $\Val^\ast \ec{u} \interp{w_j} = \Val^\ast \ec{ \const s^j_k( u )}$,
which is $\Val^\ast \ec{t}$.
If $k \neq l$, we interpret $\const s^j_k( \M( u ) )$ as the value in $\M( \tau )$ that is $\alpha$-equivalent with $\Val^\ast \ec{ t }$.
Since \rn{Cong} does not apply and due to Lemma~\ref{lem:model-completion}.3,
pairs of wrongly applied selectors are assigned the same value if and only if they reside in the same equivalence class,
and thus this definition is well-defined.

>>>>

\paragraph{Phase 3: Branching.}
If a selector is applied to a term $t$, or if $t$'s type is a finite datatype,
the equivalence class of $t$ must contain an application of one of
$\delta$'s constructors
$\Ctr^\delta = \{ \const{C}_1, \ldots, \const{C}_m \}$.
This is enforced in the third phase by the \rn{Split} rule.
A companion rule, \rn{Singleton}, handles the degenerate case where two terms
from $\tEc$ have a corecursive singleton type, in which case they must be
equivalent. Both the finiteness assumption on the datatype in \rn{Split} and
the cardinality-1 constraint on the codatatype in \rn{Singleton} are 
are computed statically
based on a recursive computation of the cardinalities of the
constructors' argument types.

@@

If $t$ is a selector term of the form $\const s^k_j( u )$,
since \rn{Split} does not apply,
$\ec{u}$ must contain a term of the form $\const C_{j'}( \const s^1_{j'}( u ), \ldots, \const s^{n}_{j'}( u ) )$ for some $j'$.
By Lemma~\ref{lem:model-completion}.2 and due to our construction of $\Val^\ast$, we have $\Val^\ast \ec{u}$ is of the form
$\MU {\Varec{u}}.\; \const C_{j'}( w_1, \ldots, w_n )$,
where $\Val^\ast \ec{u} \interp{ w_i } = \Val^\ast \ec{ \const s^i_{j'}( u )}$ for $i = 1, \ldots, n$. 
If $j = j'$, then $\M( t )$ is $\alpha$-equivalent with $\Val^\ast \ec{u} \interp{w_k}$, which is equal to $\Val^\ast \ec{ \const s^k_j( u )}$,
which is $\Val^\ast \ec{t}$.
If $j \neq j'$, we are free to interpret $\const s^k_j( \M( u ) )$ as the value in $\M( \tau )$ that is $\alpha$-equivalent with $\Val^\ast \ec{ t }$.
Since \rn{Cong} does not apply and due to Lemma~\ref{lem:model-completion}.3,
pairs of wrongly applied selectors are assigned the same value if and only if they reside in the same equivalence class,
and thus this definition is well-defined.
